Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-11 lab/report/include/lab2.tex
WriteWrite

\subsection{Task 2}
\todo[inline]{Explain our parallel version}
In listing~\ref{lst:solve} a parallelized version of the function \texttt{void Solve(double **A)} are shown. The parallelization have been done using directives from the OpenMP API. Only this function is shown as the other parts of the program for reading the input file and printing to the console is not included in the performance analysis. The approach taken for making the function execute in parallel is to distribute all the lines of the matrix evenly between all threads.

\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A)}}, label={lst:solve}]{include/solve.c}

>>>>

\todo[inline]{Comment on the prominent communication patterns in the benchmark.}

\subsection{Task 2}
\todo[inline]{Explain our parallel version}
In listing~\ref{lst:solve} a parallelized version of the function \texttt{void Solve(double **A)} are shown. The parallelization have been done using directives from the OpenMP API. Only this function is shown as the other parts of the program for reading the input file and printing to the console is not included in the performance analysis. The approach taken for making the function execute in parallel is to distribute the lines of the matrix evenly between all threads. This is done twice, once for the red dots and once for the black. Only one thread resets \texttt{diff} to zero on line 5 and test whether the program is finished or not on line 25. At each for loop that goes through the red and black dots the directive \texttt{reduction(+:diff)} is used which causes each thread to have its own private version of \texttt{diff} that all gets added together after the for loop.

\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A).}}, label={lst:solve}]{include/solve.c}
